Reinforcement Learning Produces Dominant Strategies for the Iterated Prisoner's Dilemma

### 2017-07-14 main.tex
Address Marc's comments.

% Title
\title{Reinforcement Learning Produces Dominant Strategies for the
Iterated Prisoner's Dilemma}
\author{Marc Harper \and
        Vincent Knight \and
        Martin Jones \and
        Georgios Koutsovoulos \and
        Nikoleta E. Glynatsi \and
        Owen Campbell}
\date{}

@@

In this manuscript the Axelrod library \cite{knight2016open, axelrodproject},
open source software for conducting IPD research with
reproducibility as a principal goal, is used. Written in the Python programming language,
to date the library contains source code contributed by over 50 individuals
from a variety of geographic locations and technical backgrounds. The library
is supported by a comprehensive test suite that covers all the intended
behaviors of all of the strategies in the library, as well as the features that
conduct matches, tournaments, and population dynamics.

@@

Since Robert Axelrod's seminal tournament \cite{Axelrod1980a}, a number of
IPD\@ tournaments have been undertaken and are summarised in
Table~\ref{tbl:tournaments}. Further to the work described in
\cite{knight2016open} a regular set of standard, noisy~\cite{Bendor1991} and 
probabilistic ending~\cite{Axelrod1980b} tournaments are carried out as more 
strategies are added to the Axelrod library.
Details and results are available here:
\url{http://axelrod-tournament.readthedocs.io}. This work presents a detailed
analysis of a tournament with 176 strategies (details given
in Section~\ref{sec:results}).

@@

The Axelrod library now contains many parametrised strategies trained using
machine learning
methods. Most are deterministic, use many rounds of memory, and perform
extremely well in tournaments as will be discussed in Section~\ref{sec:results}.
Training of these strategies will be discussed in Section~\ref{sec:methods}.
These strategies can encode a variety
of other strategies, including classic strategies like Tit For Tat
\cite{Axelrod1980},
handshake strategies, and grudging strategies, that always defect after
an opponent defection.

@@

\begin{figure}[!hbtp]
    \centering
    \includestandalone[height=.3\textheight]{./assets/lookerup}
    \caption{Diagrammatic representation of the Looker up Archetype.}
    \label{fig:lookerup}
\end{figure}

@@

\begin{figure}[!hbtp]
    \centering
    \includestandalone[height=.3\textheight]{./assets/gambler}
    \caption{Diagrammatic representation of the Gambler Archetype.}
    \label{fig:gambler}
\end{figure}

@@

\subsection{ANN: Single Hidden Layer Artificial Neural Network}\label{sec:ann}

@@

\begin{figure}[!hbtp]
    \centering
    \includestandalone[height=.3\textheight]{./assets/ann}
    \caption{Diagrammatic representation of the ANN Archetype.}
    \label{fig:ann}
\end{figure}

@@

\begin{figure}[!hbtp]
    \centering
    \includestandalone[height=.3\textheight]{./assets/fsm}
    \caption{Diagrammatic representation of the Finite state machine Archetype.}
    \label{fig:fsm}
\end{figure}

@@

\begin{figure}[!hbtp]
    \centering
    \begin{subfigure}[t]{.5\textwidth}
        \includegraphics[height=.3\textheight]{./assets/FSM16.pdf}
        \caption{Evolved\_FSM\_16: trained to maximise score in a standard
        tournament}
        \label{fig:fsm16}
    \end{subfigure}%
    ~
    \begin{subfigure}[t]{.5\textwidth}
        \centering
        \includegraphics[height=.35\textheight]{./assets/FSM16noise.pdf}
        \caption{Evolved\_FSM\_16\_Noise\_05: trained to maximise score in a
        noisy tournament}
        \label{fig:fsm16noise}
    \end{subfigure}%
    \caption{Trained sixteen state finite state machine players.}
    \label{fig:fsm_images}
\end{figure}

\subsection{Hidden Markov Models}\label{sec:hmm}

@@

\begin{figure}[!hbtp]
    \centering
    \includestandalone[height=.3\textheight]{./assets/hmm}
    \caption{Diagrammatic representation of the Hidden Markov Model Archetype.}
    \label{fig:hmm}
\end{figure}

@@

\begin{itemize}
  \item Players are unaware of the number of turns in a match.
  \item Players carry no acquired state between matches.
  \item Players cannot observe the outcome of other matches.
  \item Players cannot identify their opponent by any label or identifier.
  \item Players cannot manipulate or inspect their opponents in any way.
\end{itemize}

@@

The top 11 performing strategies by median payoff are all strategies trained to maximize
total payoff against a subset of the strategies (Table~\ref{tbl:standard_score}).
The next strategy is Desired Belief Strategy (DBS) \cite{Au2006},
which actively analyzes the opponent and responds
accordingly. The next two strategies are Winner12, based on a lookup table,
Fool Me Once \cite{axelrodproject}, a grudging strategy that defects indefinitely on
the second defection, and Omega Tit For Tat \cite{kendall2007iterated}.

\begin{table}[!hbtp]
        \centering
        \input{./assets/standard_top_15_scores_summary.tex}
        \caption{Standard Tournament: Mean score per turn of top 15 strategies
            (ranked by median over
        \protect\input{./assets/standard_number_of_repetitions.tex}tournaments).
        The leaderboard is dominated by the trained strategies (indicated by a
        $^{*}$).}
        \label{tbl:standard_score}
\end{table}

@@

\begin{landscape}
    \begin{figure}[!hbtp]
        \centering
        \includegraphics[width=\paperwidth]{./assets/standard_scores_boxplots.pdf}
        \caption{Standard Tournament: Mean score per turn (ranked by median
        over
        \protect\input{./assets/standard_number_of_repetitions.tex}tournaments).}
        \label{fig:standard_boxplot}
    \end{figure}
\end{landscape}

@@

\begin{figure}[!hbtp]
    \centering
    \includegraphics[width=\textwidth]{./assets/standard_scores_heatmap.pdf}
    \caption{Standard Tournament: Mean score per turn of row players against
    column players (ranked by median over
        \protect\input{./assets/standard_number_of_repetitions.tex}tournaments).}
    \label{fig:standard_heatmap}
\end{figure}

The strategies that win the most matches
(Table~\ref{tbl:standard_wins_top_winners}) are Defector~\cite{Axelrod1984} and Aggravater~\cite{axelrodproject}, followed
by handshaking and zero determinant strategies~\cite{Press2012}. 
This includes two handshaking
strategies that were the result of training to maximize Moran process fixation
(TF1 and TF2). No strategies were trained specifically to win matches. None of
the top scoring strategies appear in the top 15 list of strategies ranked by
match wins. This can be seen in Figure~\ref{fig:standard_winplot} where the
distribution of the number of wins of each strategy is shown.

\begin{table}[!hbtp]
    \centering
        \input{./assets/standard_top_15_winners_wins_summary.tex}
        \caption{Standard Tournament: Number of wins per tournament
        of top 15 strategies (ranked by median wins over
        \protect\input{./assets/standard_number_of_repetitions.tex}tournaments).}
        \label{tbl:standard_wins_top_winners}
\end{table}

\begin{landscape}
    \begin{figure}[!hbtp]
        \centering
        \includegraphics[width=\paperwidth]{./assets/standard_wins_boxplots.pdf}
        \caption{Standard Tournament: number of wins per tournament (ranked by
        median over
        \protect\input{./assets/standard_number_of_repetitions.tex}tournaments).}
        \label{fig:standard_winplot}
    \end{figure}
\end{landscape}

The number of wins of the top strategies of Table~\ref{tbl:standard_score} are
shown in Table~\ref{tbl:standard_wins}. It is evident that although these
strategies score highly they do not win many matches: the strategy with the most
number of wins is the Evolved FSM 16 strategy that at most won 60
(\(60/175\approx34\%\)) matches in a given tournament.

\begin{table}[!hbtp]
    \centering
        \input{./assets/standard_top_15_wins_summary.tex}
        \caption{Standard Tournament: Number of wins per tournament
        of top 15 strategies (ranked by median score over
        \protect\input{./assets/standard_number_of_repetitions.tex}tournaments).}
        \label{tbl:standard_wins}
\end{table}

@@

\begin{table}[!hbtp]
    \centering
        \input{./assets/standard_top_15_ranks_summary.tex}
        \caption{Standard Tournament: Rank in each tournament
        of top 15 strategies (ranked by median over
        \protect\input{./assets/standard_number_of_repetitions.tex}tournaments).}
        \label{tbl:standard_ranks}
\end{table}

\begin{landscape}
    \begin{figure}[!hbtp]
        \centering
        \includegraphics[width=\paperwidth]{./assets/standard_ranks_boxplots.pdf}
        \caption{Standard Tournament: rank in each tournament (ranked by
        median over
        \protect\input{./assets/standard_number_of_repetitions.tex}tournaments).}
        \label{fig:standard_ranks_boxplot}
    \end{figure}
\end{landscape}

@@

    \caption{Comparison of cooperation rates for Standard Tournament Top 3
    (over 10000 repetitions).}
    \label{fig:comparison_cooperation_heatmaps_standard}
\end{figure}

@@

\begin{landscape}
    \begin{figure}[!hbtp]
        \centering
        \includegraphics[width=\paperwidth]{./assets/noisy_scores_boxplots.pdf}
        \caption{Noisy (5\%) Tournament: Mean score per turn (ranked by median
        over
        \protect\input{./assets/noisy_number_of_repetitions.tex}tournaments).}
        \label{fig:noisy_score}
    \end{figure}
\end{landscape}

@@

\begin{figure}[!hbtp]
    \centering
    \includegraphics[width=\textwidth]{./assets/noisy_scores_heatmap.pdf}
    \caption{Noisy (5\%) Tournament: Mean score per turn of row players against
    column players (ranked by median over
        \protect\input{./assets/noisy_number_of_repetitions.tex}tournaments).}
    \label{fig:noisy_heatmap}
\end{figure}

As shown in Table~\ref{tbl:noisy_wins_top_winners} and
Figure~\ref{fig:noisy_winplot} the strategies tallying the most wins are
somewhat similar to the standard tournaments, with Defector, the handshaking
CollectiveStrategy~\cite{Li2009}, and Aggravate appearing as the top three again.

\begin{table}[!hbtp]
    \centering
        \input{./assets/noisy_top_15_winners_wins_summary.tex}
        \caption{Noisy (5\%) Tournament: Number of wins per tournament
        of top 15 strategies (ranked by median wins over
        \protect\input{./assets/noisy_number_of_repetitions.tex}tournaments).}
        \label{tbl:noisy_wins_top_winners}
\end{table}

\begin{landscape}
    \begin{figure}[!hbtp]
        \centering
        \includegraphics[width=\paperwidth]{./assets/noisy_wins_boxplots.pdf}
        \caption{Noisy (5\%) Tournament: number of wins per tournament (ranked by
        median over
        \protect\input{./assets/noisy_number_of_repetitions.tex}tournaments).}
        \label{fig:noisy_winplot}
    \end{figure}
\end{landscape}

As shown in Table~\ref{tbl:noisy_wins}, the top ranking strategies win a larger
number of matches in the presence of noise. For example Spiteful Tit For Tat~\cite{Prison1998} 
in one tournament won almost all its matches (167).

\begin{table}[!hbtp]
    \centering
        \input{./assets/noisy_top_15_wins_summary.tex}
        \caption{Noisy (5\%) Tournament: Number of wins per tournament
        of top 15 strategies (ranked by median score over
        \protect\input{./assets/noisy_number_of_repetitions.tex}tournaments).}
        \label{tbl:noisy_wins}
\end{table}

@@

\begin{table}[!hbtp]
    \centering
        \input{./assets/noisy_top_15_ranks_summary.tex}
        \caption{Noisy (5\%) Tournament: Rank in each tournament
        of top 15 strategies (ranked by median over
        \protect\input{./assets/noisy_number_of_repetitions.tex}tournaments).}
        \label{tbl:noisy_ranks}
\end{table}

\begin{landscape}
    \begin{figure}[!hbtp]
        \centering
        \includegraphics[width=\paperwidth]{./assets/noisy_ranks_boxplots.pdf}
        \caption{Noisy (5\%) Tournament: rank in each tournament (ranked by
        median over
        \protect\input{./assets/noisy_number_of_repetitions.tex}tournaments).}
        \label{fig:noisy_ranks_boxplot}
    \end{figure}
\end{landscape}

@@

    \caption{Comparison of cooperation rates for the Noisy (5\%) Tournament Top 3
    (over 10000 standard tournaments).}
    \label{fig:comparison_cooperation_heatmaps_noisy}
\end{figure}

@@

\begin{itemize}
    \item Particle Swarm Algorithm: \cite{imran2013overview}.
    \item Evolutionary algorithm: \cite{moriarty1999evolutionary}.
\end{itemize}

@@

\begin{itemize}
 \item total or mean payoff,
 \item total or mean payoff difference (unused in this work),
 \item total Moran process wins (fixation probability). This lead to the
     strategies named TF1, TF2, TF3 listed in
     Appendix~\ref{app:list_of_players}.
\end{itemize}

These can be used in noisy or standard environments (as evidenced by
Sections~\ref{sec:standard} and~\ref{sec:noise}). These objectives can be
further modified to suit other purposes. New strategies could be trained with
variations including spatial structure and probabilistically ending matches.

>>>>

% Title
\title{Reinforcement Learning Produces Dominant Strategies for the
Iterated Prisoner's Dilemma}
\author{Marc Harper \and
        Vincent Knight \and
        Martin Jones \and
        Georgios Koutsovoulos \and
        Nikoleta Glynatsi \and
        Owen Campbell}
\date{}

@@

This manuscript uses the Axelrod library \cite{knight2016open, axelrodproject},
open source software for conducting IPD research with
reproducibility as a principal goal. Written in the Python programming language,
to date the library contains source code contributed by over 50 individuals
from a variety of geographic locations and technical backgrounds. The library
is supported by a comprehensive test suite that covers all the intended
behaviors of all of the strategies in the library, as well as the features that
conduct matches, tournaments, and population dynamics.

@@

Since Robert Axelrod's seminal tournament \cite{Axelrod1980a}, a number of
IPD\@ tournaments have been undertaken and are summarised in
Table~\ref{tbl:tournaments}. Further to the work described in
\cite{knight2016open} a regular set of standard, noisy and probabilistic ending
tournaments are carried out as more strategies are added to the Axelrod library.
Details and results are available here:
\url{http://axelrod-tournament.readthedocs.io}. This work presents a detailed
analysis of a tournament with 176 strategies (details given
in Section~\ref{sec:results}).

@@

The Axelrod library now contains many parametrised strategies trained using
machine learning
methods. Most are deterministic, use many rounds of memory, and perform
extremely well in tournaments as will be discussed in Section~\ref{sec:results}.
Training of these strategies will be discussed in Section~\ref{sec:methods}.
These strategies can encode a variety
of other strategies, including classic strategies like Tit For Tat
\cite{Axelrod1980},
handshake strategies, and grudging strategies that always defect after
an opponent defection.

@@

\begin{figure}[!hbtp]
    \centering
    \includestandalone[height=.3\textheight]{./assets/lookerup}
    \caption{Diagrammatic representation of the Looker up Archetype}
    \label{fig:lookerup}
\end{figure}

@@

\begin{figure}[!hbtp]
    \centering
    \includestandalone[height=.3\textheight]{./assets/gambler}
    \caption{Diagrammatic representation of the Gambler Archetype}
    \label{fig:gambler}
\end{figure}

@@

\subsection{ANN: Single Hidden Layer Artificial Neural Network}

@@

\begin{figure}[!hbtp]
    \centering
    \includestandalone[height=.3\textheight]{./assets/ann}
    \caption{Diagrammatic representation of the ANN Archetype}
    \label{fig:ann}
\end{figure}

@@

\begin{figure}[!hbtp]
    \centering
    \includestandalone[height=.3\textheight]{./assets/fsm}
    \caption{Diagrammatic representation of the Finite State Machine Archetype}
    \label{fig:fsm}
\end{figure}

@@

\begin{figure}[!hbtp]
    \centering
    \begin{subfigure}[t]{.5\textwidth}
        \includegraphics[height=.3\textheight]{./assets/FSM16.pdf}
        \caption{Evolved\_FSM\_16: trained to maximise score in a standard
        tournament}
        \label{fig:fsm16}
    \end{subfigure}%
    ~
    \begin{subfigure}[t]{.5\textwidth}
        \centering
        \includegraphics[height=.35\textheight]{./assets/FSM16noise.pdf}
        \caption{Evolved\_FSM\_16\_Noise\_05: trained to maximise score in a
        noisy tournament}
        \label{fig:fsm16noise}
    \end{subfigure}%
    \caption{Trained sixteen state Finite State Machine players}
    \label{fig:fsm_images}
\end{figure}

\subsection{Hidden Markov Models}

@@

\begin{figure}[!hbtp]
    \centering
    \includestandalone[height=.3\textheight]{./assets/hmm}
    \caption{Diagrammatic representation of the Hidden Markov Model Archetype}
    \label{fig:hmm}
\end{figure}

@@

\begin{itemize}
  \item Players are unaware of the number of turns in a match
  \item Players carry no acquired state between matches
  \item Players cannot observe the outcome of other matches
  \item Players cannot identify their opponent by any label or identifier
  \item Players cannot manipulate or inspect their opponents in any way
\end{itemize}

@@

The top 11 performing strategies by median payoff are all strategies trained to maximize
total payoff against a subset of the strategies (Table~\ref{tbl:standard_score}).
The next strategy is Desired Belief Strategy (DBS) \cite{Au2006}.
which actively analyzes the opponent and responds
accordingly. The next two strategies are Winner12, based on a lookup table,
Fool Me Once \cite{axelrodproject}, a grudging strategy that defects indefinitely on
the second defection, and Omega Tit For Tat \cite{kendall2007iterated}.

\begin{table}[!hbtp]
        \centering
        \input{./assets/standard_top_15_scores_summary.tex}
        \caption{Standard Tournament: Mean score per turn of top 15 strategies
            (ranked by median over
        \protect\input{./assets/standard_number_of_repetitions.tex}tournaments).
        The leaderboard is dominated by the trained strategies (indicated by a
        $^{*}$)}
        \label{tbl:standard_score}
\end{table}

@@

\begin{landscape}
    \begin{figure}[!hbtp]
        \centering
        \includegraphics[width=\paperwidth]{./assets/standard_scores_boxplots.pdf}
        \caption{Standard Tournament: Mean score per turn (ranked by median
        over
        \protect\input{./assets/standard_number_of_repetitions.tex}tournaments)}
        \label{fig:standard_boxplot}
    \end{figure}
\end{landscape}

@@

\begin{figure}[!hbtp]
    \centering
    \includegraphics[width=\textwidth]{./assets/standard_scores_heatmap.pdf}
    \caption{Standard Tournament: Mean score per turn of row players against
    column players (ranked by median over
        \protect\input{./assets/standard_number_of_repetitions.tex}tournaments)}
    \label{fig:standard_heatmap}
\end{figure}

The strategies that win the most matches
(Table~\ref{tbl:standard_wins_top_winners} are Defector and Aggravater, followed
by handshaking and zero determinant strategies. This includes two handshaking
strategies that were the result of training to maximize Moran process fixation
(TF1 and TF2). No strategies were trained specifically to win matches. None of
the top scoring strategies appear in the top 15 list of strategies ranked by
match wins. This can be seen in Figure~\ref{fig:standard_winplot} where the
distribution of the number of wins of each strategy is shown.

\begin{table}[!hbtp]
    \centering
        \input{./assets/standard_top_15_winners_wins_summary.tex}
        \caption{Standard Tournament: Number of wins per tournament
        of top 15 strategies (ranked by median wins over
        \protect\input{./assets/standard_number_of_repetitions.tex}tournaments)}
        \label{tbl:standard_wins_top_winners}
\end{table}

\begin{landscape}
    \begin{figure}[!hbtp]
        \centering
        \includegraphics[width=\paperwidth]{./assets/standard_wins_boxplots.pdf}
        \caption{Standard Tournament: number of wins per tournament (ranked by
        median over
        \protect\input{./assets/standard_number_of_repetitions.tex}tournaments)}
        \label{fig:standard_winplot}
    \end{figure}
\end{landscape}

The number of wins of the top strategies of Table~\ref{tbl:standard_wins} are
shown in Table~\ref{tbl:standard_wins}. It is evident that although these
strategies score highly they do not win many matches: the strategy with the most
number of wins is the Evolved FSM 16 strategy that at most won 60
(\(60/175\approx34\%\)) matches in a given tournament.

\begin{table}[!hbtp]
    \centering
        \input{./assets/standard_top_15_wins_summary.tex}
        \caption{Standard Tournament: Number of wins per tournament
        of top 15 strategies (ranked by median score over
        \protect\input{./assets/standard_number_of_repetitions.tex}tournaments)}
        \label{tbl:standard_wins}
\end{table}

@@

\begin{table}[!hbtp]
    \centering
        \input{./assets/standard_top_15_ranks_summary.tex}
        \caption{Standard Tournament: Rank in each tournament
        of top 15 strategies (ranked by median over
        \protect\input{./assets/standard_number_of_repetitions.tex}tournaments)}
        \label{tbl:standard_ranks}
\end{table}

\begin{landscape}
    \begin{figure}[!hbtp]
        \centering
        \includegraphics[width=\paperwidth]{./assets/standard_ranks_boxplots.pdf}
        \caption{Standard Tournament: rank in each tournament (ranked by
        median over
        \protect\input{./assets/standard_number_of_repetitions.tex}tournaments)}
        \label{fig:standard_ranks_boxplot}
    \end{figure}
\end{landscape}

@@

    \caption{Comparison of cooperation rates for Standard Tournament Top 3
    (over 10000 repetitions)}
    \label{fig:comparison_cooperation_heatmaps_standard}
\end{figure}

@@

\begin{landscape}
    \begin{figure}[!hbtp]
        \centering
        \includegraphics[width=\paperwidth]{./assets/noisy_scores_boxplots.pdf}
        \caption{Noisy (5\%) Tournament: Mean score per turn (ranked by median
        over
        \protect\input{./assets/noisy_number_of_repetitions.tex}tournaments)}
        \label{fig:noisy_score}
    \end{figure}
\end{landscape}

@@

\begin{figure}[!hbtp]
    \centering
    \includegraphics[width=\textwidth]{./assets/noisy_scores_heatmap.pdf}
    \caption{Noisy (5\%) Tournament: Mean score per turn of row players against
    column players (ranked by median over
        \protect\input{./assets/noisy_number_of_repetitions.tex}tournaments)}
    \label{fig:noisy_heatmap}
\end{figure}

As shown in Table~\ref{tbl:noisy_wins_top_winners} and
Figure~\ref{fig:noisy_winplot} the strategies tallying the most wins are
somewhat similar to the standard tournaments, with Defector, the handshaking
CollectiveStrategy, and Aggravate appearing as the top three again.

\begin{table}[!hbtp]
    \centering
        \input{./assets/noisy_top_15_winners_wins_summary.tex}
        \caption{Noisy (5\%) Tournament: Number of wins per tournament
        of top 15 strategies (ranked by median wins over
        \protect\input{./assets/noisy_number_of_repetitions.tex}tournaments)}
        \label{tbl:noisy_wins_top_winners}
\end{table}

\begin{landscape}
    \begin{figure}[!hbtp]
        \centering
        \includegraphics[width=\paperwidth]{./assets/noisy_wins_boxplots.pdf}
        \caption{Noisy (5\%) Tournament: number of wins per tournament (ranked by
        median over
        \protect\input{./assets/noisy_number_of_repetitions.tex}tournaments)}
        \label{fig:noisy_winplot}
    \end{figure}
\end{landscape}

As shown in Table~\ref{tbl:noisy_wins}, the top ranking strategies win a larger
number of matches in the presence of noise. For example Spiteful Tit For Tat in
one tournament won almost all its matches (167).

\begin{table}[!hbtp]
    \centering
        \input{./assets/noisy_top_15_wins_summary.tex}
        \caption{Noisy (5\%) Tournament: Number of wins per tournament
        of top 15 strategies (ranked by median score over
        \protect\input{./assets/noisy_number_of_repetitions.tex}tournaments)}
        \label{tbl:noisy_wins}
\end{table}

@@

\begin{table}[!hbtp]
    \centering
        \input{./assets/noisy_top_15_ranks_summary.tex}
        \caption{Noisy (5\%) Tournament: Rank in each tournament
        of top 15 strategies (ranked by median over
        \protect\input{./assets/noisy_number_of_repetitions.tex}tournaments)}
        \label{tbl:noisy_ranks}
\end{table}

\begin{landscape}
    \begin{figure}[!hbtp]
        \centering
        \includegraphics[width=\paperwidth]{./assets/noisy_ranks_boxplots.pdf}
        \caption{Noisy (5\%) Tournament: rank in each tournament (ranked by
        median over
        \protect\input{./assets/noisy_number_of_repetitions.tex}tournaments)}
        \label{fig:noisy_ranks_boxplot}
    \end{figure}
\end{landscape}

@@

    \caption{Comparison of cooperation rates for the Noisy (5\%) Tournament Top 3
    (over 10000 standard tournaments)}
    \label{fig:comparison_cooperation_heatmaps_noisy}
\end{figure}

@@

\begin{itemize}
    \item Evolutionary algorithm: \cite{moriarty1999evolutionary}.
    \item Particle Swarm Algorithm: \cite{imran2013overview}.
\end{itemize}

@@

\begin{itemize}
 \item total or mean payoff
 \item total or mean payoff difference (unused in this work)
 \item total Moran process wins (fixation probability). This lead to the
     strategies named TF1, TF2, TF3 listed in
     Appendix~\ref{app:list_of_players}.
\end{itemize}

These can be used in Noisy or Standard environments (as evidenced by
Sections~\ref{sec:standard} and~\ref{sec:noisy}). These objectives can be
further modified to suit other purposes. New strategies could be trained with
variations including spatial structure and probabilistically ending matches.
